\documentclass{exam}
\usepackage[utf8]{inputenc}
\title{\bf Homework 3}
\author{\bf Rylan Schaeffer and Vincent Yang}

\begin{document}
\pagestyle{headandfoot}
\runningheadrule
\firstpageheader{ECS 198}{Centralized and Decentralized Cryptography}{April 21, 2016}
\runningheader{ECS 198}
              {Homework 3, Page \thepage\ of \numpages}
              {April 21, 2016}
\firstpagefooter{}{}{}
\runningfooter{}{}{}
\begin{tabular}{rl}
Name:  & \rule{0.25\linewidth}{\linethickness} \\ 
Date:  & \rule{0.25\linewidth}{\linethickness} \\ 
\end{tabular}
\vspace{5mm}

\begin{center} 
  \Large Homework 3
\end{center} 

\begin{center}
	\fbox{\parbox{5.5in}{\centering
	Answer the questions in the spaces provided.
	If you run out of room for an answer, continue on the back of the page
	}}
\end{center}

\addpoints
\begin{center}
\gradetable[h][questions]
\end{center}


\begin{questions}

  \question[3]
  Which of the following is NOT an advantage to centralization?
  \begin{choices}
    \choice Automation
    \choice Centralized Monitoring
    \choice Easy money laundering
    \choice Centralized Policy
    \choice Easily update/change cryptographic schemes
  \end{choices}

  \question[3]
  Circle the two incentives to be mine.
  \begin{choices}
    \choice Transaction Fees
    \choice Satoshi
    \choice Proof of Stake
    \choice Mining Reward
    \choice Zero-confirmation Transaction
  \end{choices}

  \question[5] The process of verifying clients' identity is called \fillin[KYC; Know Your Customer]. 

  \question[5] \fillin[Liberty Reserve/E-Gold] and \fillin[Liberty Reserve/E-Gold] were popularly used for money laundering and subsequently shut down.

  \question[5] A \fillin[Sybil Attack] is an attack in which a system is subverted by creating fake identities in a peer-to-peer network.

  \question[25] How did CentralizedCoin solve the double spending problem?
  \fillwithlines{.8in}

  \question[10] What is the difference between anonymity and pseudonymity?
  \fillwithlines{.8in}

  \question[20] What was the problem with pseudonymity in regard to E-Gold?
  \fillwithlines{1.2in}

  \question[20] What is the Byzantine Generals problem?
  \fillwithlines{1.2in}
\end{questions}
\end{document}
