\documentclass{exam}
\usepackage[utf8]{inputenc}
\title{\bf Homework 1}
\author{\bf Rylan Schaeffer and Vincent Yang}

\begin{document}
\pagestyle{headandfoot}
\runningheadrule
\firstpageheader{ECS 198}{Digital Signatures}{April 7, 2016}
\runningheader{ECS 198}
              {Homework 1, Page \thepage\ of \numpages}
              {April 7, 2016}
\firstpagefooter{}{}{}
\runningfooter{}{}{}
\begin{tabular}{rl}
Name:  & \rule{0.25\linewidth}{\linethickness} \\ 
Date:  & \rule{0.25\linewidth}{\linethickness} \\ 
\end{tabular}
\vspace{5mm}

\begin{center} 
  \Large Homework 1
\end{center} 

\begin{center}
	\fbox{\parbox{5.5in}{\centering
	Answer the questions in the spaces provided.
	If you run out of room for an answer, continue on the back of the page
	}}
\end{center}

\addpoints
\begin{center}
\gradetable[h][questions]
\end{center}



\begin{questions}

  \question[12] 
  What is the purpose of Diffie-Hellman?
  \fillwithlines{.8in}

  \question[10]
  What is the difference between symmetric and asymmetric cryptography?
  \fillwithlines{1.2in}

  \question[10]
  What is a trapdoor function?
  \fillwithlines{1.2in}


  \question[3]
  What is a synonym for asymmetric encryption?
  \begin{choices}
    \choice Advanced Encryption System (AES)
    \choice Public-key Cryptography 
    \choice Caesar Cipher
    \choice Secret-key Cryptography
  \end{choices}

  \question[3]
  What is a synonym for symmetric encryption?
  \begin{choices}
    \choice Advanced Encryption System (AES)
    \choice Public-key Cryptography 
    \choice Secret-key Cryptography
    \choice Cyber Security
  \end{choices}

  \question[10]
  What is the definition of Perfect Forward Secrecy?
  \fillwithlines{1.2in}

  \question[5] The \fillin[Message Space] is the set of possible messages.

  \question[5] If you want to make information secret, hide its existence
  or make it \fillin[intelligible].

  \question[17]
  What are the two properties of Digital Signatures and why are they important?
  \fillwithlines{2in}

  \question[25] I am performing a Diffie Hellman Key Exchange with you. Given prime numbers 3 and 5, and secret numbers 18 and 23, 
  what is our shared key?
  \vspace{\stretch{5}}


\end{questions}
\end{document}
