\documentclass{exam}
\usepackage[utf8]{inputenc}
\title{Homework 1}
\author{Vincent Yang}

\begin{document}
\pagestyle{headandfoot}
\runningheadrule
\firstpageheader{ECS 198}{Digital Signatures}{April 7, 2016}
\runningheader{ECS 198}
              {Homework 1, Page \thepage\ of \numpages}
              {April 7, 2016}
\firstpagefooter{}{}{}
\runningfooter{}{}{}
\begin{tabular}{rl}
Name:  & \rule{0.25\linewidth}{\linethickness} \\ 
Date:  & \rule{0.25\linewidth}{\linethickness} \\ 
\end{tabular}
\vspace{5mm}

\begin{center} 
  \Large Homework 1
\end{center} 

\begin{center}
	\fbox{\parbox{5.5in}{\centering
	Answer the questions in the spaces provided.
	If you run out of room for an answer, continue on the back of the page
	}}
\end{center}

\addpoints
\begin{center}
\gradetable[h][questions]
\end{center}



\begin{questions}

  \question[12] 
  What is the purpose of Diffie-Hellman?
  \fillwithlines{1.2in}
	\vspace{\stretch{1}}


  \question[3]
  What is a Merkle-Damgard transform?
  \begin{choices}
    \choice A type of tree in which hashes are combined to make a root that can be used to verify
    a hash's existence.
    \choice A method of transforming variable length inputs to fixed length outputs
    \choice A method of exchanging private keys publically
    \choice A bitstring, determined by implementation, that the first block gets hashed with in SHA-256
  \end{choices}

  \question[3]
  What is the pigeonhole principle?
  \begin{choices}
    \choice A method of brute force searching for Cryptographic Hash collisions
    \choice A method of verifying a hash output given a key and message
    \choice The state of having spread-out outputs for a Cryptographic Hash Function
    \choice The idea that if the input sample space is larger than output sample space, collisions must exist
  \end{choices}

  \question[3] The \fillin[Birthday Paradox] is a phenomenon in which the probability of collisions rises much faster than expected.
    
  \question[3] A \fillin[Search Puzzle] is a math problem that requires searching a large amount to find a solution without shortcuts
  \question[10]
  What is the difference between Symmetric and Asymmetric Encryption?
  \fillwithlines{1.2in}
	\vspace{\stretch{1}}

  \question[16]
  What are the two properties of Digital Signatures and why are they important?
  \fillwithlines{2in}
	\vspace{\stretch{1}}



  \question[15]
  What are the three properties of Cryptographic Hash Functions and why are they important?
  \fillwithlines{2in}
	\vspace{\stretch{1}}

  \question[10]
  What is the point of message digests?
  \fillwithlines{.5in}
  \vspace{\stretch{1}}

  \question[25] I am performing a Diffie Hellman Key Exchange with you. Given prime numbers 3 and 5, and secret numbers 18 and 23, 
  what is our shared key?
  \vspace{\stretch{5}}


\end{questions}
\end{document}
